---
title: "Exercise  4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exploring the count tables

Here, import an example count table and do some exploration of the expression data. 

```{r exSetup1, eval=FALSE}
counts_file <- system.file("extdata/rna-seq/SRP029880.raw_counts.tsv",
                           package = "compGenomRData")
coldata_file <- system.file("extdata/rna-seq/SRP029880.colData.tsv", 
                            package = "compGenomRData")
```

1. Normalize the counts using the TPM approach. 
```{r}
library(compGenomRData)
library(pheatmap)
library(stats)
library(corrplot)

counts_file <- system.file("extdata/rna-seq/SRP029880.raw_counts.tsv", package = "compGenomRData")
coldata_file <- system.file("extdata/rna-seq/SRP029880.colData.tsv",
                            package = "compGenomRData")
counts <- as.matrix(read.table(counts_file, header = T, sep = '\t'))
geneLengths <- as.vector(subset(counts, select = c(width)))
rpk <- apply( subset(counts, select = c(-width)), 2,
              function(x) x/(geneLengths/1000))
tpm <- apply(rpk, 2, function(x) x / sum(as.numeric(x)) * 10^6)

#2

V <- apply(tpm, 1, var)
selectedGenes<- names(V[order(V, decreasing = T)][1:500])
pheatmap(tpm[selectedGenes,], scale = 'row', show_rownames = FALSE)

V <- apply(tpm, 1, var)
selectedGenes<- names(V[order(V, decreasing = T)][1:100])
pheatmap(tpm[selectedGenes,], scale = 'row', show_rownames = FALSE)
```

3. Re-do the heatmaps setting the `scale` argument to `none`, and `column`. Compare the results with `scale = 'row'`.
```{r}
pheatmap(tpm[selectedGenes,], scale = 'none', show_rownames = FALSE)
pheatmap(tpm[selectedGenes,], scale = 'column', show_rownames = FALSE)
```
4. Draw a correlation plot for the samples depicting the sample differences as 'ellipses', drawing only the upper end of the matrix, and order samples by hierarchical clustering results based on `average` linkage clustering method. 
```{r}
correlationMatrix <- cor(tpm)
corrplot(correlationMatrix, order = 'hclust',
         addrect = 2, addCoef.col = 'white',
         number.cex = 0.7)
```

### Git and Github

5. Open Github account, and install git if it required as instructed in the following link: https://github.com/llendway/github_for_collaboration/blob/master/github_for_collaboration.md

6. Create a repository and commit and push the answers of this exercise through Rtudio (Please upload the answers to the exercises also to Moodle).

7. Insert the link to your Github account here.
https://github.com/Theophmann/Theo_test_repo.git